IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/real.tex
Macro fix
cowl

\begin{figure}[t]
\centerline{\includegraphics[width=0.7\columnwidth]{figs/node}}
\caption{\label{fig:node}
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
\subsubsection{Server-side Node.js IFC:}\ 
We have implemented |specLangJS seqf| for Node.js in the form of a
library, without modifying Node.js or the V8 JavaScript engine.
%
Our implementation\footnote{Available at \codelink{}.} provides a
library for creating new tasks, i.e., contexts whose global object
only contains the standard JavaScript library and our IFC primitives
(e.g., |send| and |sandbox|).
%
When mapped to our formal treatement, |sandbox| is defined with |ap
klone tS = tS0|, where |tS0| is the global object corresponding to the
standard JavaScript library and our IFC primitives.
%
%These tasks can communicate and create new tasks, in turn.
%
These IFC operations are mediated by the trusted library code (executing
as the main Node.js context), which tracks the state (current label, messages,
etc.) of each task.  An example for |send|/|recv| is shown in
Figure~\ref{fig:node}.
%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
We remark that our system conservatively restricts
the kinds of messages that can be exchanged, via |send| (and |sandbox|),
to string values.
%
(We provide a convenience library which marshalls JSON objects to/from strings.)
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%

While the described system implements |specLangJS seqf|, applications
typically require access to libraries (e.g., the file system library
\textsf{fs}) that that have external effects.
%
Exposing the Node.js APIs directly to sandboxed tasks is unsafe.
Instead, we implement libraries such as a labeled \textsf{fs} as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
the IFC monitor.
%
While this is safer than simply wrapping unsafe objects, adding
featuers such as the \textsf{fs} requires the code in the main task to
ensures that labels are properly propagated and enforced.
%
Unfortunately, while imposing such a proof burden
is undesirable, this also has to be expected:
different language environments expose different libraries for
handling external I/O, and the correct treatment of external effects
is application specific.
%
%% For instance, in the case of Node.js, how labels interact with the
%% file system may even vary according to the application (e.g.,
%% in the IFC system Hails~\cite{hails}, labels are not persisted).
%
%While we can extend our formalism to model a particular interface to
%the file system, HTTP client, etc. the utility of this formalization is
%unclear and left to future work.
%
We do not extend our formalism to account for the  particular
interface to the file system, HTTP client, etc., as this is
specific to the Node.js implementation and does not generalize
to other systems.

\subsubsection{Client-side COWL IFC:}\
We now describe some of the implementation aspects of
COWL, a JavaScript implementation of coarse-grained
IFC for Mozilla's Gecko.  This work provides the formal basis for
the implementation, and COWL is described in much more detail in~\cite{swapi}.
%
Since the architecture of COWL is similar to that of Node.js, we focus
on the main differences.

%Tasks in COWL  correspond to browsing contexts, such as iframes,
%where the global object |tS0| also contains the DOM, the
%\verb|XMLHttpRequest| (XHR) object, etc.
%
Existing browser APIs offer \emph{web workers}, which can
be spawned by JavaScript code and have
the same isolation properties as tasks in our system.
%
The isolation of web workers was motivated by the lack of multithreading
in JavaScript; however, their isolation properties are equally useful for information
flow control.

To ensure that JavaScript code cannot communicate using the global object
(e.g., to the network with XHR or persistent storage using the DOM),
COWL additionally uses content security policy (CSP)~\cite{csp1.1}.\footnote{
  Since CSP does not yet restrict message-passing or navigation, this
  was addressed explicitly in the implementation.
}
%
Note, that this does not prevent tasks from manipulating the DOM
(e.g., to render information), so external effects due to DOM access
are also suppressed.
%
Simply disallowing all external effects for all browsing contexts is
overly-restricting; pages typically load images, perform XHR requests
to dynamically load data,
etc.
%
Hence, COWL allows
controlled network communication (inter-frame communication is
dictated by our |send| rule) by associating an implicit label with a
remote host: namely the label corresponding to its origin.
%
In turn, when a task perform a request, the COWL runtime performs the
same label check as that of |send|, namely that the task label can
flow to
the remote origin label.

Once again, while the external effects of COWL can be formally modeled,
we do not model these effects in our more general framework, since, like
for Node.js case, they are application specific.
%
%Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
%though they're both JavaScript systems, simply because of the
%differing environments.

>>>>

\begin{figure}[t]
\centerline{\includegraphics[width=0.7\columnwidth]{figs/node}}
\caption{\label{fig:node}
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
\paragraph{Server-side with Node.js:}
We have implemented |specLangJS seqf| for Node.js in the form of a
library, without modifying Node.js or the V8 JavaScript engine.
%
Our implementation\footnote{Available at \codelink{}.} provides a
library for creating new tasks, i.e., contexts whose global object
only contains the standard JavaScript library and our IFC primitives
(e.g., |send| and |sandbox|).
%
When mapped to our formal treatement, |sandbox| is defined with |ap
klone tS = tS0|, where |tS0| is the global object corresponding to the
standard JavaScript library and our IFC primitives.
%
%These tasks can communicate and create new tasks, in turn.
%
These IFC operations are mediated by the trusted library code (executing
as the main Node.js context), which tracks the state (current label, messages,
etc.) of each task.  An example for |send|/|recv| is shown in
Figure~\ref{fig:node}.
%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
We remark that our system conservatively restricts
the kinds of messages that can be exchanged, via |send| (and |sandbox|),
to string values.
%
(We provide a convenience library which marshalls JSON objects to/from strings.)
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%

While the described system implements |specLangJS seqf|, applications
typically require access to libraries (e.g., the file system library
\textsf{fs}) that that have external effects.
%
Exposing the Node.js APIs directly to sandboxed tasks is unsafe.
Instead, we implement libraries such as a labeled \textsf{fs} as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
the IFC monitor.
%
While this is safer than simply wrapping unsafe objects, adding
features such as the \textsf{fs} requires the code in the main task to
ensures that labels are properly propagated and enforced.
%
Unfortunately, while imposing such a proof burden
is undesirable, this also has to be expected:
different language environments expose different libraries for
handling external I/O, and the correct treatment of external effects
is application specific.
%
%% For instance, in the case of Node.js, how labels interact with the
%% file system may even vary according to the application (e.g.,
%% in the IFC system Hails~\cite{hails}, labels are not persisted).
%
%While we can extend our formalism to model a particular interface to
%the file system, HTTP client, etc. the utility of this formalization is
%unclear and left to future work.
%
We do not extend our formalism to account for the  particular
interface to the file system, HTTP client, etc., as this is
specific to the Node.js implementation and does not generalize
to other systems.

\paragraph{Client-side with COWL:}
This work provides the formal basis for the core part of the COWL
client-side JavaScript IFC system~\cite{swapi}.
%
Like our Node.js implementation, COWL takes a coarse-grained approach
to providing IFC for JavaScript programs.
%
Unlike our implementation, however, COWL's IFC monitor is implemented in
the browser layout engine (though still leaving the JavaScript engine
unmodified).

Furthermore, COWL repurposes existing contexts (e.g., iframes and
pages) as IFC tasks, only imposing additional constraints on how they
communicate.
%
Much like Node.js case, at its core, the global object of a COWL task
should only contain the standard JavaScript libraries and
\texttt{postMessage}, whose semantics are modeled by our
\textsc{JS-send} rule.
%
However, existing contexts have objects such as the DOM and COWL must
ensure that a task's external effects are restricted.
%
To this end, any communication (even via the DOM) is mediated at
the context boundary by COWL.

Simply disallowing all external effects for is overly-restricting for
real-world applications (e.g., pages typically load images, perform
XHR requests etc.).
%
Hence, COWL allows safe network communication by associating an
implicit label with remote hosts (a host's label corresponds to
its origin).
%
In turn, when a task perform a request, the COWL IFC monitor
ensures that the task label can flow to the remote origin label.
%
While the external effects of COWL can be formally modeled, we do not
model these effects in our more general framework, since, like for
Node.js case, they are specific to this system.
%
%Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
%though they're both JavaScript systems, simply because of the
%differing environments.
